Forecasting the 2024 U.S. Presidential Election through Poll Aggregation and Adjustments for Poll Quality

### 2024-11-04 paper/paper.qmd
add limit on prediction

## Insights on Polling and Election Dynamics

@@

## Limitations of the Model

@@

@@

# Election Prediction

>>>>

## Polling and Election Dynamics

@@

## Limitations of the Model {#sec-model-limitations}

@@

## Limitation of the Prediction

In @sec-prediction, the team predicted that Kamala Harris would secure 298 delegates while Donald Trump would obtain 240 delegates. However, this prediction has several limitations. Firstly, the model used to generate these predictions inherits the constraints outlined in  @sec-model-limitations. Additionally, the predictions are based on averaging results from polling data for each state, which can lead to propagated prediction errors.

Each state has a limited number of polls available; while the overall analysis considered a substantial number of polls, individual states often had fewer than 20 polls, with even the largest states contributing only up to 27. Moreover, as noted in Section @sec-prediction, the analysis focused solely on closely contested races, specifitatiocally swing states. Consequently, many states were assigned to a candidate based on strong historical trends rather than direct predictions. Although this approach is reasonable, it may overlook emerging trends that could potentially shift a state's allegiance from Republican to Democrat or vice versa.

@@

# Election Prediction {#sec-prediction}
